Rice yield improvements by plant breeding are offset by decreases over time

### 2017-05-11 output/breed_paper.Rnw
Updates paper

Yield was modeled as a response to the number of years since the
variety was officially released using a mixed-effects linear
model. Differences between years and cultivars were included in the
model as random effects according to:

\begin{equation}
 yield_i = \alpha + \beta_{years\ since\ release\ i}* x_{years\ since\
   release\ i} + \beta_{release\ year\ i}*x_{release\ year\ i} + \beta_{year\ i} + \beta_{cultivar\ i}
\end{equation}

Where $yield_i$ is the grain yield for plot $i$, $\alpha$ is the
average yield for the RES across varieties and years (intercept),
$\beta_{years\ since\ release\ i}$ is effect of $x_{years\ since\
release\ i}$, the number of years $i$'s cultivar has been in the
trials (negative for years prior to release, zero at the year of
release), $\beta_{release\ year\ i}$ is the effect of $x_{release\
year\ i}$, the year of release for $i$'s cultivar, $\beta_{year}$ is
the random effect of year, and $\beta_{cultivar}$ is the random effect
of cultivar.

@@

legend("bottomright", legend = c("w/ years since release",
                                 "w/o years since release",
                                 "90% Credible interval"),
       lty = c(1,2, NA),
       bty = "n",
       fill = c(NA,NA, "grey"),
       border = NA,
       merge = TRUE)
polygon(x = c(yrs, rev(yrs)),
        y = c(ints[1,],rev(ints[2,])),
        border = NA,
        col = rgb(0,0,0,0.1))

@@

% \begin{figure}[h]

>>>>

Yield was modeled as a response to the number of years since the
variety was officially released using a mixed-effects linear
model. Differences between years and cultivars were included in the

%
% model as random effects according to:

% \begin{equation}
%  yield_i = \alpha + \beta_{years\ since\ release\ i}* x_{years\ since\
%    release\ i} + \beta_{release\ year\ i}*x_{release\ year\ i} + \beta_{year\ i} + \beta_{cultivar\ i}
% \end{equation}

% Where $yield_i$ is the grain yield for plot $i$, $\alpha$ is the
% average yield for the RES across varieties and years (intercept),
% $\beta_{years\ since\ release\ i}$ is effect of $x_{years\ since\
% release\ i}$, the number of years $i$'s cultivar has been in the
% trials (negative for years prior to release, zero at the year of
% release), $\beta_{release\ year\ i}$ is the effect of $x_{release\
% year\ i}$, the year of release for $i$'s cultivar, $\beta_{year}$ is
% the random effect of year, and $\beta_{cultivar}$ is the random effect
% of cultivar.

@@

legend("bottomright", legend = c("w/ years since release adj.",
                                 "w/o years since release adj.",
                                 "90% Credible interval"),
       lty = c(1,2, NA),
       bty = "n",
       fill = c(NA,NA, "grey"),
       border = NA,
       merge = TRUE,
       cex = 0.8)
polygon(x = c(yrs, rev(yrs)),
        y = c(ints[1,],rev(ints[2,])),
        border = NA,
        col = rgb(0,0,0,0.1))

@@

<<echo=FALSE, results=tex>>=
ids = aggregate(release_yr ~ id, data = mod_data, unique)
colnames(ids) = c("Cultivar", "Release Year")
ids = ids[order(ids[,2]),]
ids[,2] = as.integer(ids[,2])
ids[,1] = gsub("M", "M-", ids[,1])

print(xtable(ids,
             caption = "All named medium grain rice cultivars and their associated release year planted at the Rice Experiment Station (RES), Biggs, California from 1984 -- 2015.",
             label = "tbl:ids"),
      include.rownames = FALSE,
      booktabs = TRUE,
      caption.placement = "top")
@ 
% \begin{figure}[h]
